Approximation as Differentiation: Notes

### 2025-05-24 notes.tex
Sync notes summary.

\title{Approximation as Differentiation}

\author{Robert Atkey}
\email{robert.atkey@strath.ac.uk}
\orcid{0000-0002-4414-5047}
\affiliation{%
  \institution{University of Strathclyde}
  \city{Glasgow}
  \country{UK}}

\author{Roly Perera}
\email{roly.perera@cl.cam.ac.uk}
\orcid{0000-0001-9249-9862}
\affiliation{%
  \institution{University of Cambridge}
  \city{Cambridge}
  \country{UK}
}
\additionalaffiliation{%
   \institution{University of Bristol}
   \city{Bristol}
   \country{UK}
}

@@

\section{Notes}

@@

Covered so far:
\begin{itemize}
\item automatic differentiation (\secref{auto-diff})
\item $\CMon$-enriched categories, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\item category $\Fam(I,\cat{C})$ of $I$-indexed families of objects of $\cat{C}$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{\cat{C}}F$ and category of families $\Fam(\cat{C})$
(\secref{grothendieck})
\item useful categories of families for automatic approximation
(\secref{galois-slicing-auto-diff-via-fam}):
   \begin{itemize}
      \item Galois slicing via $\Fam(\LatGal)$ (\secref{galois-slicing-auto-diff-via-fam:galois-slicing})
      \item automatic differentiation via $\Fam(\FinVect)$ (\secref{galois-slicing-auto-diff-via-fam:auto-diff})
   \end{itemize}
\end{itemize}

@@

\input{notes/preliminaries}
\input{notes/auto-diff}
\input{notes/cmon}
\input{notes/cmon-enriched}
\input{notes/biproduct}
\input{notes/useful-semi-additive-categories}
\input{notes/fam}
\input{notes/set-indexed-product}
\input{notes/grothendieck}
\input{notes/auto-diff-galois-slicing-via-fam}
\input{notes/language}

>>>>

\title{Approximation as Differentiation: Notes}

@@

@@

Covered here:
\begin{itemize}
\item automatic differentiation (\secref{auto-diff})
\item stable functions (\secref{stable-functions})
\item $\CMon$, the category of commutative monoids (\secref{cmon})
\item $\CMon$-enrichment, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\item category $\Fam(I,\cat{C})$ of $I$-indexed families of objects of $\cat{C}$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{\cat{C}}F$ and category of families $\Fam(\cat{C})$
(\secref{grothendieck})
\item useful categories of families for automatic approximation
(\secref{galois-slicing-auto-diff-via-fam}):
   \begin{itemize}
      \item Galois slicing via $\Fam(\LatGal)$ (\secref{galois-slicing-auto-diff-via-fam:galois-slicing})
      \item automatic differentiation via $\Fam(\FinVect)$ (\secref{galois-slicing-auto-diff-via-fam:auto-diff})
   \end{itemize}
\end{itemize}

@@

\input{notes/preliminaries}
\input{notes/auto-diff}
\input{notes/stability}
\input{notes/cmon}
\input{notes/cmon-enriched}
\input{notes/biproduct}
\input{notes/useful-semi-additive-categories}
\input{notes/fam}
\input{notes/set-indexed-product}
\input{notes/grothendieck}
\input{notes/auto-diff-galois-slicing-via-fam}

\input{notes/language}
